ManuscriptPURFits

### 2024-03-11 Code/Plots_PURFits.Rmd
made "P" italic in legend

@@

  scale_linetype_manual(values = c("solid", "dashed"), labels = c("P value < 0.05", "P value > 0.05")) +

>>>>

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x)))}

@@

  scale_linetype_manual(values = c("solid", "dashed"), labels = c(italic("P") ~ "value <0.05", italic("P") ~ "value >0.05")) +
